Simplifying Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-08-08 article.rnw
Change the word "correctness" to "accuracy".

We propose that species might be best partitioned into groups without regard to any \emph{a priori} definition but instead based purely upon which grouping gives the most parsimonious model.
Such data-informed grouping approaches have previously proved successful in other contexts, such as finding modules in networks \parencite{guimera2005functional,newman2006modularity,girvan2002community}.
In this study, we investigate the usefulness and correctness of such an \emph{a posteriori} approach using experimental data from competition between different \emph{Drosophila} species provided by \textcite{terry2021natural}.
We fit a Lotka--Volterra competition model to these data to find the groupings that give the most parsimonious model, and we then compare these groupings to similarity based upon a species trait (body size).
While doing so, we group species independently with regard to their effects upon other species and their responses to other species to find whether the data-informed groupings differ between these two cases.

>>>>

We propose that species might be best partitioned into groups without regard to any \emph{a priori} definition but instead based purely upon which grouping gives the most parsimonious model.
Such data-informed grouping approaches have previously proved successful in other contexts, such as finding modules in networks \parencite{guimera2005functional,newman2006modularity,girvan2002community}.
In this study, we investigate the usefulness and accuracy of such an \emph{a posteriori} approach using experimental data from competition between different \emph{Drosophila} species provided by \textcite{terry2021natural}.
We fit a Lotka--Volterra competition model to these data to find the groupings that give the most parsimonious model, and we then compare these groupings to similarity based upon a species trait (body size).
While doing so, we group species independently with regard to their effects upon other species and their responses to other species to find whether the data-informed groupings differ between these two cases.
